SecFFT: Safeguarding Federated Fine-tuning for Large Vision Language Models against Covert Backdoor Attacks in IoRT Networks

### 2024-11-04 response.tex

\hypersetup{
pdfauthor = {\myAuthorsShort},
pdftitle = {\myTitle},
pdfsubject = {\myJournal\xspace},
colorlinks = true,
linkcolor=black!70!green, 
citecolor=black!70!green,       
filecolor=magenta,      
urlcolor=black!70!black           
}

\begin{document}

\thispagestyle{plain}

 {\Large We would like to thank the editor for the time and effort to gather insightful reviews for our submission to IEEE Internet of Things Journal (IoT-41947-2024: \textbf{\textit{ SecFFT: Safeguarding Federated Fine-tuning for Large Vision Language Models against Covert Backdoor Attacks in IoRT Networks}}). In response to the comments from the Editor and the reviewers, we have revised the paper extensively. We also would like to thank the Editor and the reviewers for the valuable and constructive comments that help us improve the quality of the paper significantly. The followings are the detailed answers to the comments. %It is also noted that, we add the letter ` `R'' (i.e., Response) before the reference number of references which are added in this response, e.g., ``[R1]'', and ``[R2]''. This is to distinguish references in this response letter and those in the revised paper.
 It is also noted that, as the whole manuscript has undergone substantial and comprehensive revisions, to facilitate clarity for the reviewers, we have marked the newly added or completely rewritten parts in {\color{blue}blue\color{black}} within the revised manuscript. The remaining sections, where only language and expression changes have been made, are still presented in black text.
 }

@@

%\end{abstract}

\newpage

%=================================
%=================================
\section{Summary of changes}
Based on the valuable feedback from the reviewers, we have made significant improvements to the manuscript in the following areas:
\color{red}
\begin{itemize}

\item \textbf{Enhancement of Figure Visuals and Annotations:} We improved the legibility and resolution of some figures by increasing font size and image clarity, especially for data-heavy visuals, where overlapping graph sections required enhanced contrast and color differentiation. Essential labels and legends were added to facilitate clearer interpretation of each figure, which significantly improves readability and accessibility.

\item \textbf{Detailed Explanations of Algorithm Steps and Variable Definitions:} We expanded on each algorithm step to ensure the procedures were explicitly defined and coherent. Clarifications included the purpose and function of each step, removal of unused variables, and further detailing of essential variables’ roles. These improvements enhance accuracy and clarity in the algorithmic section, enabling better comprehension of the method.

\item \textbf{Experiment Design and Result Analysis:} The experimental section was refined to provide in-depth information on experimental design, including hyper-parameter choices and defense strategy comparisons. We added specific explanations for quantitative metrics (e.g., ACC, AUC) to support statistical validity, enabling clearer insight into each defense mechanism's effectiveness across various scenarios.

\item \textbf{Simplification of Language and Improvement of Logical Flow:} Language revisions were made to enhance readability, simplifying complex expressions and avoiding lengthy technical jargon. Improvements in logical flow were applied both within paragraphs and between sections, ensuring smooth transitions that enhance the paper’s coherence without sacrificing technical detail.

\item \textbf{Consistency in Symbol Usage and Standardization of Formulas:} To eliminate potential ambiguity, we standardized the use of symbols and formatting of formulas, following academic conventions for mathematical expressions. This consistency supports clarity, allowing readers to focus on the technical content without distraction.

\item \textbf{Supplementary Explanations of Technical Concepts and Novel Contributions:} We expanded explanations for key terms and highlighted the paper's unique contributions over existing methods. These additions emphasize the research's significance and potential applications, giving readers a comprehensive understanding of the advancements presented in the study.

% \item Figures and Tables: we improved figure clarity, resolution, and font size to enhance readability. We added labels and adjusted layouts to ensure figures are legible, and we reformatted tables to meet layout requirements without compromising content visibility.

% \item Algorithm Details: we provided detailed explanations for each step in the algorithm, removed unused variables, and aligned descriptions with algorithm steps. These changes improve accuracy and coherence within the methodology section.

% \item Experimental Analysis:we added quantitative analysis and provided explanations for metrics (e.g., ACC, AUC) used in the experiments. Additionally, we included a rationale for hyper-parameter choices to improve transparency and clarify the experimental setup.

% \item Language and Expression: we revised language for clarity and fluency, corrected grammatical errors, and simplified complex expressions to enhance readability and overall text quality.

% \item Consistency and Symbol Usage: we standardized figure referencing and corrected inconsistent or incorrect symbol usage to ensure coherence and accuracy throughout the manuscript.

% % 根据Reviewer 1's Comment 1，Comment 2以及Reviewer 2's Comment 1，我们修改了文章的部分公式以及重新构建了符号表，使文章的公式符号的意义更加清晰，优化阅读体验。
% \item \textbf{[Writing and expression:]} Based on \textbf{Reviewer 1's Comment 1, Comment 2}, and \textbf{Reviewer 2's Comment 1}, we have revised some of the formulas in the paper and reconstructed the symbol table to make the meanings of the formula symbols clearer and to enhance the overall reading experience.

% % 根据Reviewer 1's Comment 3，我们对Threat models部分的基本假设做了进一步的假设，使得本文提出的概念更便于理解。
% \item \textbf{[Threat Models:]} Based on \textbf{Reviewer 1's Comment 3}, we made further assumptions in the \textbf{Threat Models} section regarding the basic assumptions, making the concepts proposed in this paper easier to understand.

% % 根据Reviewer 1's Comment 4，我们增加了额外的实验来说明了采样大小和模型准确率之间的关系。

% % 根据Reviewer 1's Comment 5, 我们对DUPLEX PRIVACY AMPLIFICATION的auxiliary downlink privacy obfuscation部分做了修改，澄清了“社区导向框架”与"异质性情景下提高效率的意义“”之间联系。
% \item \textbf{[Duplex privacy amplification:]} Based on \textbf{Reviewer 1's Comment 5}, we revised the \textbf{Auxiliary downlink privacy obfuscation} section of \textbf{Duplex privacy amplification}, clarifying the connection between the \textbf{community-oriented framework} and the \textbf{significance of improving efficiency in heterogeneous scenarios}.

% % 根据Reviewer 2's Comment 2，
% \item \textbf{[Credit-based active poisoning resistance:]} Based on \textbf{Reviewer 2's Comment 5}, we supplemented the consideration of resource consumption by adding an analysis of communication efficiency and computational time complexity.

% % 根据Reviewer 2's Comment 3，我们对experimental Environment部分进行了相应的修改，解释了实验部分针对不同数据集选择对应模型结构和超参数的原因。根据Reviewer 2's Comment 4， 我们在实验结果描述部分添加了对CIFAR-100的实验结果以及相应的分析。
% \item \textbf{[Performance evaluation:]} Based on \textbf{Reviewer 2's Comment 3}, we made corresponding revisions to the \textbf{Experimental environment} section of \textbf{Performance evaluation}, explaining the rationale behind selecting the appropriate model structures and hyperparameters for different datasets in the experiments. Additionally, in response to \textbf{Reviewer 2's Comment 4}, we added the experimental results for CIFAR-100, along with the corresponding analysis, to the experimental results description section. Furthermore, in response to \textbf{Reviewer 1's Comment 4}, We conducted additional experiments to illustrate the relationship between sample size and model accuracy.

@@

% % comment7
% %...

% \newpage
% ```
\section{Responses to the Comments from Reviewer 1}

% comment6
\rcomment{
\color{red} The text in some experimental result figures is too small to be legible. Improving the clarity and resolution is recommended.
}

\textbf{Response:} Thank you for your valuable feedback regarding the legibility of the experimental result figures. We have reviewed each figure in the manuscript and enhanced the resolution and clarity to ensure that all text and details are easily readable. Specifically, we have increased the font size within the figures and adjusted the image quality to provide a sharper, more distinct presentation of the experimental results.

% Figure \ref{fig:lab2} shows a image after modification. We also updated the corresponding analysis in the article to better align with the experimental findings and enhance readability. The revised analysis is shown below:

% \textcolor{blue}{SecFFT outperforms other mechanisms in handling various attack. SecFFT achieves the lowest misidentification rate, at only 0.2\%, indicating its superior defense capability and robustness across various attack scenarios, accurately distinguishing between malicious and benign nodes. Conversely, the misidentification rates of Flame, FLTrust, and FoolsGold are 8\%, 3.9\%, and 9.5\%, respectively, with misidentified nodes more broadly distributed. Among them, FoolsGold exhibits the highest misidentification rate. It is worth noting that these statistical results align precisely with the findings from the previous experiment, further validating SecFFT's superior performance in instantaneous Attack Behavior Perception.}

@@

% 感谢您指出文本中描述行数与算法不一致的问题。我们已根据算法的最新修改，仔细检查并修正了第五节最后一段中的行数描述，确保其与算法2的步骤完全对齐。具体来说，我们逐条对照了算法中的每个步骤，确保每个操作、条件和循环都在文本中得到了准确反映。

% 此外，我们在修订过程中还增强了描述的清晰度，以便读者能够更容易理解算法的执行流程。我们还添加了必要的背景信息和解释，以帮助读者在上下文中更好地理解每一步的意义和目的。

% 这些修改不仅提高了文本的准确性，也增强了整篇论文的逻辑连贯性。我们非常感谢您对此问题的关注，这使我们能够提升稿件的整体质量和可读性。

\textbf{Response:} Thank you for pointing out the inconsistency between the line numbers described in the text and those in Algorithm 2. We have carefully reviewed and revised the final paragraph of Section 5 to ensure that it aligns perfectly with the updated steps in the algorithm. Specifically, we compared each step in the algorithm with the corresponding actions, conditions, and loops described in the text to ensure accurate representation.

@@

    \item \textbf{"for Each point $O_j \neq O_i$ do"}: We clarified that this loop iterates over all points in the dataset except for point $O_i$, and we specified the purpose of comparing each $O_j$ with $O_i$ in the context of the algorithm’s objective.
\end{itemize}

% 除此之外，我们还发现了一个小细节，即原本的注释中注释符号和注释内容左右空格数量不一致，我们顺便修复了这个错误。

In addition, we also discovered a small detail that the number of spaces left and right in the original comments was inconsistent between the comment symbols and the comment content. We also fixed this error.

These modifications provide a more detailed and precise description of the algorithm’s flow. We appreciate your insights and believe these clarifications enhance the readability and understanding of Algorithm 2.
% 现在的算法2伪代码如下所示：
% TODO: 现在有一个问题就是，文章中的算法2在Response中出现更早，因此编号变成了Algorithm 1
The pseudocode after modification for Algorithm 2 is as \ref{alg:malicious-node-detection-history}.

\begin{algorithm}[!t]
\caption{Attack intention detection and secure aggregation}
\label{alg:malicious-node-detection-history}
\begin{algorithmic}[1]
\State \textbf{Input:} Global model history $\{\theta_g^{t-T}, \dots, \theta_g^{t-1}\}$, historical gradient updates for each client $\{\triangledown \theta_{i}^{t-T}, \dots, \triangledown \theta_{i}^{t-1}\}$
\State \textbf{Output:} Sets of normal clients $U_{nor}$ and malicious clients $U_{mal}$

@@

% \For {Client $i$}
%     \State Compute $lof_i = \frac{\sum_{j \in Nei_i} \frac{lrd_j}{lrd_i}}{|Nei_i|}$
%     \If {$lof_i > 1$}
%         \State Mark client $i$ as malicious, add to $U_{mal}$
%     \Else
%         \State Mark client $i$ as normal, add to $U_{nor}$
%     \EndIf
% \EndFor
% \State $U_{mal} = \{i \,|\, lof_i > 1\}$
% \State $U_{nor} = \{i \,|\, lof_i \leq 1\}$
\State $U_{mal}, U_{nor}  \gets \{i \,|\, lof_i > 1\}, \{i \,|\, lof_i \leq 1\}$

\State{\color{CadetBlue}/* \textbf{Secure aggregation of global FFT model */}} 
        \State $cre_i'  \gets \tanh(cre_i)$\Comment{Compute adjusted confidence}
        \State $w_i  \gets \frac{cre_i'}{\sum_{i \in U_{nor}} cre_i'}$\Comment{Normalize weights}
\EndFor

\State \textbf{Output:} $\theta_g^t \gets \theta_g^{t-1} + \sum_{i \in U_{nor}} w_i \cdot \triangledown \theta_i^t$\Comment{Aggregate global model}
\end{algorithmic}
\end{algorithm}

\newpage
% comment10
\rcomment{
\color{red} Section VI-C lacks quantitative analysis of the experimental results. The partitioning results in Fig. 6 are hard to distinguish, and the font size is too small. Moreover, the four subplots lack necessary labels, and the same issues are present in Fig. 7.
}
\textbf{Response:} 
Thank you for your valuable comments and suggestions, which have greatly helped us to improve our paper. We have carefully addressed each of the issues you raised and made the following modifications:

First, we recognized the need for a more in-depth quantitative analysis in this section. We have now included additional statistical data to provide a comprehensive analysis of the experimental results, including metrics that better quantify the effectiveness of our method. This has been added to enhance the clarity and significance of our findings.
The following are the corresponding modifications in the article:

@@

\newpage

\section{Responses to the Comments from Reviewer 2}

% comment17
\rcomment{
\color{red} The concept of intent recognition is a key innovation in this manuscript’s. However, the definition and construction of attacker intent are vague and need further elaboration to help readers better understand the core idea.
}

% 感谢您对我们手稿中意图识别概念的深刻评论。我们认识到清晰地定义和构建攻击者意图的重要性，因为这是我们研究中的一个关键创新。

% 为了解决您的担忧，我们在修订的手稿中详细阐述了攻击者意图的定义。具体来说，我们现在包括：

% 明确的定义：我们提供了攻击者意图的简明定义，解释了它在我们研究中的相关性及其对威胁评估和响应策略的影响。

% 意图的构建：我们详细说明了攻击者意图在我们的框架中是如何构建的，概述了促成其识别的因素。这包括行为模式、上下文线索以及用于推断意图的数据驱动方法。

% 示例和场景：我们增加了说明性示例和场景，展示意图识别在现实世界中的应用，增强读者对其实际应用的理解。

% 与现有模型的比较：为了进一步阐明我们的方法，我们将意图识别的概念与现有模型进行了比较，强调了我们的框架的创新之处和优势。

% 我们感谢您的反馈，这对我们改进这一部分内容有很大帮助。我们相信，这些增强将使读者对我们工作的核心思想——攻击者意图识别有更清晰、更全面的理解。

\textbf{Response:}

Thank you for your insightful comments regarding the concept of intent recognition in our manuscript. We recognize the importance of clearly defining and constructing the notion of attacker intent, as it is a pivotal innovation in our research.

To address your concerns, we have elaborated on the definition of attacker intent in the revised manuscript. Specifically, we now include:

\begin{enumerate}
    \item \textbf{Clear Definition}: We provide a concise definition of attacker intent, explaining its relevance in the context of our study and its implications for threat assessment and response strategies.

    \item \textbf{Construction of Intent}: We detail how attacker intent is constructed within our framework, outlining the factors that contribute to its identification. This includes the behavioral patterns, contextual clues, and data-driven approaches used to infer intent.

    \item \textbf{Examples and Scenarios}: We have added illustrative examples and scenarios that demonstrate how intent recognition can be applied in real-world situations, enhancing readers’ understanding of its practical applications.

    \item \textbf{Comparison with Existing Models}: To further clarify our approach, we compare our concept of intent recognition with existing models, highlighting the innovations and advantages of our framework.
\end{enumerate}

We appreciate your feedback, which has significantly contributed to the improvement of this section. We believe that these enhancements will provide readers with a clearer and more comprehensive understanding of the core idea of attacker intent recognition in our work.

% 我们对“意图点”的解释如下：

Our explanation of the ``intention" is as follows:

\textcolor{blue}{In our proposed framework, the concept of the "intention point" serves as a pivotal element in recognizing the underlying motives of malicious nodes during the federated fine-tuning process. The intention point is defined as the central position within a high-dimensional space, representing the aggregated gradient updates of a client across multiple training rounds. This point encapsulates the client's intended direction for influencing the global model. To construct the intention point, we utilize a Minimum Enclosing Hypersphere approach, which encompasses a proportion of the client’s gradient updates. The radius of this hypersphere reflects the reliability of the intention point, effectively quantifying the client's consistency in updating the model. By analyzing these intention points, our method can discern the behaviors of malicious clients from benign ones, enhancing the overall security and robustness of the federated learning system.}

% comment18
\rcomment{
\textcolor{red} The description of the experiments is unclear. The titles and text in the figures are too small, making them difficult to read. For example, in Fig. 5, the data curves are hard to distinguish. It is recommended to enlarge key areas to better present the experimental results and analysis. Additionally, many figures lack sufficient explanation.
}
\textbf{Response:} 
% 对于第一个实验：Model integrity and poisoning resistance，我们重新整理了相应数据，并修改了图片的表现形式。修改包括对图例字体格式以及大小的修改，同时为图中折现重合的部分加上了子图，使其更容易辨别。同时，我们也修改了原文中对于该实验结果的描述，使其更符合实验数据，同时更易于阅读和理解。
Thank you for your detailed feedback regarding the clarity of our experimental descriptions and figures. We have carefully revised the manuscript to address each of the issues you raised.

@@

The corresponding modifications in the article are as follows:

As depicted in the figure, in all attack scenarios, SecFFT consistently achieves an attack success rate (ASR) close to zero, while the test success accuracy (TSR) remains high. \textcolor{blue}{This indicates that SecFFT effectively defends against attacks by accurately identifying and neutralizing malicious users, all while preserving the performance and accuracy of the global model. In contrast, other defense mechanisms perform less effectively. Although Flame also shows strong performance in reducing ASR and mitigating malicious attack, it introduces considerable noise in the identification process, leading to a decrease in TSR, especially under MR attacks, where the performance degradation is more pronounced. FLTrust fails to defend effectively, with ASR initially low in MR attacks but quickly rising after several iterations, ultimately proving ineffective; against NEUR and EDGE CASE attacks, ASR remains high from the outset, demonstrating inadequate defense. Foolsgold also shows poor performance in defending against all three types of attacks, maintaining a high ASR from the beginning. Overall, the comparison highlights that other defense mechanisms either fail to effectively resist attacks or compromise model performance during defense. This further underscores SecFFT's significant advantage in federated fine-tuning for backdoor attack resistance, making it the optimal defense choice.}

% comment19
\rcomment{
\color{red} For the third paragraph of left column on page 9, several "steps" are mentioned but not explained in the text.
}

### 2024-11-04 main-v2.tex
archive: responsed all

\section{System model \& Preliminaries}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%symbols 表格
\begin{table}[!t]
{
\renewcommand{\arraystretch}{1.2}
\caption{Summary of Main Notation}
\label{notations}
\vspace{0em}
\centering
\begin{tabular}{| c || p{6cm}  |}
\hline
\textbf{Symbol} & \multicolumn{1}{c |}{\textbf{Description}}\\
    \hline
    $ N $ & The number of nodes participating in each round.\\ \hline
    $R_i$ & The $i$-th robot node. \\ \hline
    $D_i$ & The private local dataset of node $R_i$.\\ \hline
    $\theta_g^t, \theta_i^t$ & The global model and local model of $R_i$ at round $t$. \\ \hline
    $\triangledown \theta_i^t$ & Local update of $R_i$ during round $t$. \\ \hline
    $G_i^t $ & Frequency vector of $R_i$'s update at round $t$. \\ \hline
    $m$ & The length of the low-frequency vectors. \\ \hline
    $H^t$ & The matrix formed by stacking $G_i^t$. \\ \hline
    $\tilde{G}^t $ & The extracted global clean ingredient at round $t$. \\ \hline
    $\lambda_{max}^t$ & The largest singular value of matrix $H^t$ at round $t$. \\ \hline
    $\xi_{max}^t$ & The left singular vector corresponding to $\lambda_{max}^t$. \\ \hline
    $Chi_i^t$ & The difference between $\triangledown \theta_i^t$ and $\tilde{G}^t $ at round $t$. \\ \hline
    $t'$ & The round number within total $T$ rounds. \\ \hline
    $O_i^{t'}$ & The intention point of $R_i$ at round $t'$. \\ \hline
    \( {v}_{i}^{t'} \) & The vector of the behavior ray for $R_i$ at round $t'$. \\ \hline
    $lof_i$ & The outlier level of $R_i$.\\ \hline
    $cre_i$ & The credit score of $R_i$.\\ \hline
\end{tabular}
    }
 \vspace{-1.5em}
 \end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsubsection{Construction of attack intention}
% 这个问题可以抽象为高维空间中的一些具有起点的射线。射线的起点代表上轮次的全局模型，射线的方向代表本轮次展平后的更新变化。问题的优化目标是：找到一个最小的超球，至少覆盖$\zeta$比例的射线。
This problem can be abstracted as rays in a high-dimensional space with specific starting points. The starting point of a ray represents the global model from the previous round, and the direction of the ray represents the flattened update in the current round. The optimization goal of the problem is to find a minimum hypersphere that covers at least a $\zeta$ proportion of the rays.
% 我们使用符号$O_i$代表客户端$i$在高维空间中超球的球心，使用符号$r_i$代表这个超球的半径。假设当前轮次为$t$，$t'$是最近$T$轮次中的其中一轮，使用符号$\tilde O_i^{t'}$代表球心到第$t'$对应射线的最近点。则可以定义优化问题：
We use the symbol $O_i$ to represent the center of the hypersphere for client $i$ in the high-dimensional space and $r_i$ to represent the radius of this hypersphere. Suppose the current round is $t$, and $t'$ is one of the recent $T$ rounds. Let $\tilde O_i^{t'}$ denote the closest point from the hypersphere center to the ray corresponding to round $t'$. Then, the optimization problem can be defined as:

@@

\begin{figure}[!ht]
    \centering
    \includegraphics[width=\linewidth]{figures/fig3.png}
    \caption{Long-term attack intention detection module and secure aggregation}
    \label{fig3:longterm}
\end{figure}

@@

@@

% \textbf{攻击方式}：对于单轮恶意用户检测，我们使用包括MR\cite{MR}、EDGE CASE\cite{EDGE_CASE}、以及NEUR\cite{zhang2022neurotoxin}在内的三种针对联邦学习场景的最新攻击。MR攻击通过将中毒图像与正常图像混合来创建恶意数据集，并使用投影梯度下降法进行本地训练来达到植入后门的效果；EDGE CASE攻击利用罕见的“边缘情况”样本，通过数据或模型投毒在联邦学习模型中插入后门；Neurotoxin攻击则尝试通过识别在正常节点训练中不常更新的参数，并利用这些参数插入后门，以提高后门的持久性。For Instantaneous Attack Behavior Perception,?
\textbf{Attack paradigms:} we employed three state-of-the-art attacks targeting federated learning scenarios, namely \textbf{MR}\cite{MR}, \textbf{EDGE CASE}\cite{EDGE_CASE}, and \textbf{NEUR}\cite{zhang2022neurotoxin}. The MR attack generates a malicious dataset by combining poisoned images with normal ones and employing the projected gradient descent method for local training to implant backdoors; the EDGE CASE attack employs rare "edge-case" samples to inject backdoors into the federated learning model through data or model poisoning; the NEUR attack seeks to identify parameters that are seldom updated during normal node training and uses these parameters to insert backdoors, thereby enhancing the persistence of the backdoor.

@@

% \textbf{对比算法}：对于单轮恶意用户检测算法，我们对比了三种聚合算法：FedAVG\cite{FedAVG}、FLTrust\cite{FLTrust}和Flame\cite{FLAME}。其中FedAVG根据每个节点数据集的大小对其上传的更新进行加权聚合；FLTrust利用一个干净的数据集，仅聚合那些上传更新与该干净数据集上训练所得更新余弦相似度较高的节点；而Flame则通过模型聚类和权重剪裁来估计并注入适量噪声，有效消除联邦学习中的后门攻击。
\textbf{Baseline defense mechanisms:} 
% For Instantaneous Attack Behavior Perception, we compared four aggregation algorithms: \textbf{FedAVG}\cite{FedAVG}, \textbf{Foolsgold}\cite{foolsgold}, \textbf{FLTrust}\cite{FLTrust}, and \textbf{Flame}\cite{FLAME}. FedAVG performs weighted aggregation of the updates uploaded by each node based on the size of their dataset; FoolsGold distinguishes between benign and malicious clients by assessing pairwise similarity among model updates, subsequently down-weighting abnormal updates on the FL server; FLTrust uses a clean dataset and only aggregates updates from nodes whose updates have a high cosine similarity with the updates obtained from the clean dataset; Flame estimates and injects an appropriate amount of noise through model clustering and weight clipping to effectively eliminate backdoor attacks in federated learning.
we compared four aggregation mechanisms: \textbf{FedAVG}\cite{FedAVG}, \textbf{Foolsgold}\cite{foolsgold}, \textbf{FLTrust}\cite{FLTrust}, and \textbf{Flame}\cite{FLAME}. FedAVG conducts weighted aggregation of updates uploaded by each node based on the size of its dataset. FoolsGold differentiates between benign and malicious clients by evaluating pairwise similarity among model updates and subsequently down-weighting anomalous updates on the FL server. FLTrust employs a clean dataset and aggregates only those updates from nodes that exhibit high cosine similarity with the updates derived from the clean dataset. Flame estimates and injects an appropriate amount of noise via model clustering and weight clipping to mitigate backdoor attacks in federated learning effectively.

>>>>

\section{System model \& Preliminaries}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%symbols 表格
\begin{table}[!t]
{
\renewcommand{\arraystretch}{1.2}
\caption{Summary of Main Notation}
\label{notations}
\vspace{0em}
\centering
\begin{tabular}{| c || p{6cm}  |}
\hline
\textbf{Symbol} & \multicolumn{1}{c |}{\textbf{Description}}\\
    \hline
    $ N $ & The number of nodes participating in each round.\\ \hline
    $R_i$ & The $i$-th robot node. \\ \hline
    $D_i$ & The private local dataset of node $R_i$.\\ \hline
    $\theta_g^t, \theta_i^t$ & The global model and local model of $R_i$ at round $t$. \\ \hline
    $\triangledown \theta_i^t$ & Local update of $R_i$ during round $t$. \\ \hline
    $G_i^t $ & Frequency vector of $R_i$'s update at round $t$. \\ \hline
    $m$ & The length of the low-frequency vectors. \\ \hline
    $H^t$ & The matrix formed by stacking $G_i^t$. \\ \hline
    $\tilde{G}^t $ & The extracted clean ingredient at round $t$. \\ \hline
    $\lambda_{max}^t$ & The largest singular value of matrix $H^t$ at round $t$. \\ \hline
    $\xi_{max}^t$ & The left singular vector corresponding to $\lambda_{max}^t$. \\ \hline
    $Chi_i^t$ & The difference between $\triangledown \theta_i^t$ and $\tilde{G}^t $ at round $t$. \\ \hline
    $t'$ & The round number within total $T$ rounds. \\ \hline
    $O_i^{t'}$ & The intention point of $R_i$ at round $t'$. \\ \hline
    \( {v}_{i}^{t'} \) & The vector of the behavior ray for $R_i$ at round $t'$. \\ \hline
    $lof_i$ & The outlier level of $R_i$.\\ \hline
    $cre_i$ & The credit score of $R_i$.\\ \hline
\end{tabular}
    }
 \vspace{-1.5em}
 \end{table}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

\subsubsection{Construction of attack intention}
% 这个问题可以抽象为高维空间中的一些具有起点的射线。射线的起点代表上轮次的全局模型，射线的方向代表本轮次展平后的更新变化。问题的优化目标是：找到一个最小的超球，至少覆盖$\zeta$比例的射线。
This problem can be abstracted as rays in a high-dimensional space with specific starting points. The starting point of a ray represents the global model from the previous round, and the direction of the ray represents the flattened update in the current round. The optimization goal of the problem is to find a minimum hypersphere that covers at least a $\zeta$ proportion of the rays. \textcolor{red}{Among them, $\ zeta $is to avoid interference from excessively outlier rays}.
% 我们使用符号$O_i$代表客户端$i$在高维空间中超球的球心，使用符号$r_i$代表这个超球的半径。假设当前轮次为$t$，$t'$是最近$T$轮次中的其中一轮，使用符号$\tilde O_i^{t'}$代表球心到第$t'$对应射线的最近点。则可以定义优化问题：
We use the symbol $O_i$ to represent the center of the hypersphere for client $i$ in the high-dimensional space and $r_i$ to represent the radius of this hypersphere. Suppose the current round is $t$, and $t'$ is one of the recent $T$ rounds. Let $\tilde O_i^{t'}$ denote the closest point from the hypersphere center to the ray corresponding to round $t'$. Then, the optimization problem can be defined as:

@@

\begin{figure}[!ht]
    \centering
    \includegraphics[width=\linewidth]{figures/fig3-history.pdf}
    \caption{Long-term attack intention detection module and secure aggregation}
    \label{fig3:longterm}
\end{figure}

@@

\textcolor{red}{In our proposed framework, the concept of the "intention point" serves as a pivotal element in recognizing the underlying motives of malicious nodes during the federated fine-tuning process. The intention point is defined as the central position within a high-dimensional space, representing the aggregated gradient updates of a client across multiple training rounds. This point encapsulates the client's intended direction for influencing the global model. To construct the intention point, we utilize a Minimum Enclosing Hypersphere approach, which encompasses a proportion of the client’s gradient updates. The radius of this hypersphere reflects the reliability of the intention point, effectively quantifying the client's consistency in updating the model. By analyzing these intention points, our method can discern the behaviors of malicious clients from benign ones, enhancing the overall security and robustness of the federated learning system.}

@@

% \textbf{攻击方式}：对于单轮恶意用户检测，我们使用包括MR\cite{MR}、EDGE CASE\cite{EDGE_CASE}、以及NEUR\cite{zhang2022neurotoxin}在内的三种针对联邦学习场景的最新攻击。MR攻击通过将中毒图像与正常图像混合来创建恶意数据集，并使用投影梯度下降法进行本地训练来达到植入后门的效果；EDGE CASE攻击利用罕见的“边缘情况”样本，通过数据或模型投毒在联邦学习模型中插入后门；Neurotoxin攻击则尝试通过识别在正常节点训练中不常更新的参数，并利用这些参数插入后门，以提高后门的持久性。For Instantaneous Attack Behavior Perception,?
\textbf{Attack paradigms:} we employed three state-of-the-art attacks targeting federated learning scenarios, namely \textbf{MR}\cite{MR}, \textbf{EDGE CASE}\cite{EDGE_CASE}, and \textbf{NEUR}\cite{zhang2022neurotoxin}. The MR attack generates a malicious dataset by combining poisoned images with normal ones and employing the projected gradient descent method for local training to implant backdoors; the EDGE CASE attack employs rare "edge-case" samples to inject backdoors into the federated learning model through data or model poisoning; the NEUR attack seeks to identify parameters that are seldom updated during normal node training and uses these parameters to insert backdoors, thereby enhancing the persistence of the backdoor\color{red}{\cite{yao2022blockchain}}\color{black}{.}

@@

% \textbf{对比算法}：对于单轮恶意用户检测算法，我们对比了三种聚合算法：FedAVG\cite{FedAVG}、FLTrust\cite{FLTrust}和Flame\cite{FLAME}。其中FedAVG根据每个节点数据集的大小对其上传的更新进行加权聚合；FLTrust利用一个干净的数据集，仅聚合那些上传更新与该干净数据集上训练所得更新余弦相似度较高的节点；而Flame则通过模型聚类和权重剪裁来估计并注入适量噪声，有效消除联邦学习中的后门攻击。
\textbf{Baseline defense mechanisms:} 
% For Instantaneous Attack Behavior Perception, we compared four aggregation algorithms: \textbf{FedAVG}\cite{FedAVG}, \textbf{Foolsgold}\cite{foolsgold}, \textbf{FLTrust}\cite{FLTrust}, and \textbf{Flame}\cite{FLAME}. FedAVG performs weighted aggregation of the updates uploaded by each node based on the size of their dataset; FoolsGold distinguishes between benign and malicious clients by assessing pairwise similarity among model updates, subsequently down-weighting abnormal updates on the FL server; FLTrust uses a clean dataset and only aggregates updates from nodes whose updates have a high cosine similarity with the updates obtained from the clean dataset; Flame estimates and injects an appropriate amount of noise through model clustering and weight clipping to effectively eliminate backdoor attacks in federated learning.
we compared four aggregation mechanisms: \textbf{FedAVG}\cite{FedAVG}, \textbf{Foolsgold}\cite{foolsgold}, \textbf{FLTrust}\cite{FLTrust}, and \textbf{Flame}\cite{FLAME}. FedAVG conducts weighted aggregation of updates uploaded by each node based on the size of its dataset. FoolsGold differentiates between benign and malicious clients by evaluating pairwise similarity among model updates and subsequently down-weighting anomalous updates on the FL server. FLTrust employs a clean dataset and aggregates only those updates from nodes that exhibit high cosine similarity with the updates derived from the clean dataset. Flame estimates and injects an appropriate amount of noise via model clustering and weight clipping to mitigate backdoor attacks in federated learning effectively\color{red}{\cite{yao2024leoedge}}\color{black}{.}
